### 2017-10-15 paper/sexSelectionSpacingAppendix-ver1.tex
Minor edits
Add spell 2 & 3 parity progression graphs and fix Makefile

@@

@@

@@

@@

@@

@@

>>>>

\subsection{First Spell}

@@

% PARITY PROGRESSION SURVIVAL CURVES - Low

% Low education

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-0}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{1}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{2}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{3}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{4}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Survival curves conditional on parity progression
for women with no education by quarter (3 month period).
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_low_pps}
\end{figure}

@@

% PARITY PROGRESSION SURVIVAL - MEDIUM

% Low education

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-0}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{1}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{2}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_med_rural_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{3}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_med_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{4}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_med_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Survival curves conditional on parity progression
for women with 1-7 years of education by quarter (3 month period).
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_med_pps}
\end{figure}

@@

% PARITY PROGRESSION SURVIVAL - High education

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-0}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{1}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{2}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_rural_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{3}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{4}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Survival curves conditional on parity progression
for women with 8 or more years of education by quarter (3 month period).
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_high_pps}
\end{figure}

@@

% PARITY PROGRESSION SURVIVAL - LOW

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-0}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{1}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{2}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{3}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{4}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Survival curves conditional on parity progression
for women with no education by quarter (3 month period).
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell3_low_pps}
\end{figure}

@@

% PARITY PROGRESSION SURVIVAL - MEDIUM

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-0}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{1}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{2}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_med_rural_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{3}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_med_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{4}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_med_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Survival curves conditional on parity progression
for women with 1 to 7 years of education by quarter (3 month period).
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell3_med_pps}
\end{figure}

@@

% PARITY PROGRESSION SURVIVAL - high

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-0}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{1}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{2}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_high_rural_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{3}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_high_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{4}
\subfloat[1995--2006]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Survival curves conditional on parity progression
for women with 8 or more years of education by quarter (3 month period).
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell3_high_pps}
\end{figure}
